### 2015-03-22 doc/tutorial/introduction.Rmd
extract findbinary, add fix for svmperf

>>>>

# FAQ

## Searching for an unknown solver

If you try to find a wrapper that does not exist, FIXME: fix that.
for now the error later on:
Class 'try-error'  atomic [1:1] Error in UseMethod("findSoftware") : 
  no applicable method for 'findSoftware' applied to an object of class "c('CSVM_walltime', 'SVMWrapper')"

## FindBinary stalls

If the binary expects inputs, executing the binary will stall. Please make sure that your binary does not expect input upon being called without parameters. If necessary, turn off automatic search and provide **SVMBridge** with the direct path to the software.
FIXME: WILL SEND 1 to the program, if the program is called SVMperf. will still stall on other wait-for-key-programs.
